Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2018-10-24 ms.tex
found and removed floating 'q'
updaated ideal photodiode picture.

\author{Douglas Kelly}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA} q

@@

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{ideal_photodiode.pdf}
\caption{A cartoon schematic of a H2RG detector inspired by \citet{smith2008imgPersistence,tulloch2018persistenceH2RG}.
The green and tan regions depict the N-type and P-type semiconductors.
The undepleted zones of the semiconductor (bright green and dark blue) contain mobile charge carriers whereas the depletion region (solid green and tan zones) have no mobile carriers and all electrons are in the valence state.
The depletion region is widest after detector reset and shrinks as the detector is illuminated with photons that create electron-hole pairs.
Charged traps for negative and positive carriers (depicted as round circles) will capture charge before it can flow to the undepleted regions of the detector.}\label{fig:npSchematic}
\end{figure}

>>>>

\author{Douglas Kelly}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA}

@@

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{ideal_photodiode.pdf}
\caption{A cartoon schematic of a H2RG detector inspired by \citet{smith2008imgPersistence} and \citet{tulloch2018persistenceH2RG}.
The green and blue regions depict the N-type and P-type semiconductors.
The undepleted zones of the semiconductor (bright green and dark blue) contain mobile charge carriers whereas the depletion region (dark green) have no mobile carriers and all electrons are in the valence state.
The depletion region is widest after detector reset and shrinks as the detector is illuminated with photons that create electron-hole pairs.
The voltage can be measured non-destructively as the well fills and then reset before saturating.}\label{fig:npSchematic}
\end{figure}
